TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-01 paper/paper.tex
Minor changes

This report includes a performance and behavior analysis of different TCP congestion control algorithms in a (simulated) multitenant datacenter network. Based on the results, we will recommend datacenters on measures to keep providing a reliable environment for customers when multiple congestion control algoritms are active in the network, for example using Quality of Service or discouraging certain congestion control algorithms. The main research question is: {\it How can a datacenter provide a reliable and performant environment for customers when multiple TCP congestion control algorithms are used in the
network?}

@@

\section{Results}
	\subsection{TCP Congestion Algorithms}
	The most common TCP congestion algorithms are CTCP, CUBIC and BIC. CTCP is the default congestion algorithm in Microsoft Windows Server 2008 and newer \cite{cubic-kernel-version}. CUBIC is the default congestion algorithm in Linux distributions with kernel versions 2.6.19 and higher \cite{cubic-kernel-version}. BIC was the default congestion algorithm in earlier Linux distributions from kernel version 2.6.8 until 2.6.19 \cite{bic-kernel-version} \cite{cubic-kernel-version}. DCTCP and BBR will also be tested as those protocols are newer. DCTCP is specifically designed for datacenters \cite{dctcp-congestion} and BBR is a new congestion protocol not yet widely deployed \cite{bbr-congestion}.

>>>>

This report includes a performance and behavior analysis of different TCP congestion control algorithms in a (simulated) multitenant datacenter network. Based on the results, we will recommend datacenters on measures to take to keep providing a reliable environment for customers when multiple congestion control algoritms are active in the network, for example using Quality of Service or discouraging certain congestion control algorithms. The main research question is: {\it How can a datacenter provide a reliable and performant environment for customers when multiple TCP congestion control algorithms are used in the
network?}

@@

\section{Results}
Type some text here.

	\subsection{TCP Congestion Algorithms}
	The most common TCP congestion algorithms are CTCP, CUBIC and BIC. CTCP is the default congestion algorithm in Microsoft Windows Server 2008 and newer \cite{cubic-kernel-version}. CUBIC is the default congestion algorithm in Linux distributions with kernel versions 2.6.19 and higher \cite{cubic-kernel-version}. BIC was the default congestion algorithm in earlier Linux distributions from kernel version 2.6.8 until 2.6.19 \cite{bic-kernel-version} \cite{cubic-kernel-version}. DCTCP and BBR will also be tested as those protocols are newer. DCTCP is specifically designed for datacenters \cite{dctcp-congestion} and BBR is a new congestion protocol not yet widely deployed \cite{bbr-congestion}.
